Simulation pipeline

### 2023-11-21 Analysis/01_Simulating_spaces_and_stressors.Rmd
updated scripts

```{r, eval = FALSE}
library(devtools)
devtools::install_github("TGuillerme/dads")
devtools::install_github("TGuillerme/dispRity")
```

```{r}
library(dads)     # needs to be version >= 0.1.4
library(dispRity) # needs to be version >= 1.5.7
```

@@

## Simulating the data
simulated_data <- dads(bd.params = bd_params,
                       stop.rule = stop_rule,
                       traits    = my_trait)

@@

@@

## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")
```

@@

This one might be a bit trickier (though doable).
One way to do it (as suggested in our last meeting) could be to simply add a number of data points to places that already have data. 
However, this will result in non-comparable number of elements in each simulations.

One alternative (at least for now) would be to use the `"density"` algorithm from `dispRity::reduce.space` that will reduce the nearest neighbours distance between elements (basically making clumps of two elements close to each other).

@@

>>>>

```{r, eval = FALSE}
library(devtools)
devtools::install_github("TGuillerme/treats")
devtools::install_github("TGuillerme/dispRity")
```

```{r}
set.seed(1)
library(treats)     # needs to be version >= 0.1.4
library(dispRity) # needs to be version >= 1.5.7
```

@@

## Simulating the data
simulated_data <- treats(bd.params = bd_params,
                         stop.rule = stop_rule,
                         traits    = my_trait)

@@

```{r, fig.height = 12, fig.width = 6}
## Visualising the results
par(mfrow = c(2, 1))
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")
```

@@

@@

Using the `"density"` algorithm from `dispRity::reduce.space` that to reduce the nearest neighbours distance between elements (basically making clumps of two elements close to each other).

@@

## Paper figure

```{r}
plot.text.box <- function(my_text, ...) {
  plot(1,1, xaxt = "n", yaxt = "n", xlab = "", ylab = "", col = "white", pch = 21)
  text(c(1,1), my_text, ...)
}

pdf(file = "../Manuscript/Figures/simulation_protocol.pdf", height = 16, width = 8)
par(mfrow = c(6, 3), bty = "n")

## First line
plot.text.box("Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c("lightgrey", "blue"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

## Stressors
plot.text.box("1) Resampling\nwith stressor:\nnull mechanism", cex = 2)
plot.1D(trait_space, reduction = random_reduction, null = rep(TRUE, 200), main = "1D null mechanism", legend = c("Full distribution (200sp)", "Resample (100sp)"))
plot.2D(trait_space, reduction = random_reduction, null = !random_reduction, main = "2D null mechanism")

plot.text.box("2) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism", legend = c("Random resampling (100sp)", "Biased resampling (100sp)"))
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

plot.text.box("12) Resampling\nwith stressor:\nequalizing\nmechanism", cex = 2)
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")

plot.text.box("4) Resampling\nwith stressor:\nexcluding\nmechanism", cex = 2)
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D excluding mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D excluding mechanism")

plot.text.box("5) Resampling\nwith stressor:\nfacilitating\nmechanism", cex = 2)
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")
dev.off()
```

### 2023-11-21 Analysis/02_Simulation_pipeline.Rmd
updated scripts

```{r, eval = FALSE}
## Getting the non-CRAN (yet) libraries
library(devtools)
devtools::install_github("TGuillerme/dads")
```

```{r}
## Libraries
require(dads)
require(dispRity)
require(BAT)
require(FD)
require(ks)
require(TPD)
```

>>>>

```{r, eval = FALSE}
## Getting the non-CRAN (yet) libraries
library(devtools)
devtools::install_github("TGuillerme/treats")
install.packages(c("dispRity", "BAT", "FD", "ks", "TPD"))
```

```{r}
## Libraries
require(treats)
require(dispRity)
require(BAT)
require(FD)
require(ks)
require(TPD)
```
